### 2014-06-09 Simluations/Figures/MPA_figs.Rmd
finished simulations

```{r loadData, echo=FALSE, message=FALSE}
#sim=read.csv("~/Desktop/noMPAnotThresh_add_2013-12-09.csv")
# for emma's local copy
#sim=read.csv("/Users/efuller/Documents/Projects/Moving_fish/MovingFish/Simluations/Aspatial_fast/Data/nothresh/noMPAnotThresh_add_2013-12-09.csv")

# for synced online github data
x = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/noMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL25vTVBBbm90VGhyZXNoX2FkZF8yMDEzLTEyLTA5LmNzdiIsImV4cGlyZXMiOjEzOTI2NDYxMDl9--46e45a3eb2faef7fc22b6124253c925bd2290de9")
sim = read.csv(textConnection(x))

fish = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/fishMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2Zpc2hNUEFub3RUaHJlc2hfYWRkXzIwMTMtMTItMDkuY3N2IiwiZXhwaXJlcyI6MTM5MjY0NjE0NH0%3D--8eff4ee16d08efcf6b266c3e4e42adde7aeff969")
fishmpa = read.csv(textConnection(fish))

cons = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/consMPAnotThresh_add_2014-01-23.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2NvbnNNUEFub3RUaHJlc2hfYWRkXzIwMTQtMDEtMjMuY3N2IiwiZXhwaXJlcyI6MTM5MjY0NjE2Nn0%3D--586d3cb31ac0f1fe3c49f48886e3796b5132bb77")
consmpa = read.csv(textConnection(cons))
```

@@

```{r results}
par(mfrow=c(1,3))
noMang <- plotfig(sim); plotParams(noMang)
fish <- plotfig(fishmpa); plotParams(fish)
cons <- plotfig(consmpa); plotParams(cons)
```

>>>>

```{r loadData, echo=FALSE, message=FALSE}
# for synced online github data
x = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/MPAnull_2014-03-02.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL01QQW51bGxfMjAxNC0wMy0wMi5jc3YiLCJleHBpcmVzIjoxMzk0NDc3MzYwfQ%3D%3D--5fa73caaafffae7c95d930f61def04ee9b96930a")
sim = read.csv(textConnection(x))

fish = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/MPAfish_2014-03-02.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL01QQWZpc2hfMjAxNC0wMy0wMi5jc3YiLCJleHBpcmVzIjoxMzk0NDc3MzQ2fQ%3D%3D--9b6ceb0092173222543c95381dfbb0f42f0c884f")
fishmpa = read.csv(textConnection(fish))

cons = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/MPAcons_2014-03-01.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL01QQWNvbnNfMjAxNC0wMy0wMS5jc3YiLCJleHBpcmVzIjoxMzk0NDc3MzIwfQ%3D%3D--5f4f584256a4175eebe2ef5465e83c92ebe65cc0")
consmpa = read.csv(textConnection(cons))
```

@@

```{r results}

ggplot(consmpa, aes(speed, harvest)) + geom_tile(aes(fill=Equil.pop, alpha = cut(Equil.pop, breaks=c(0,1, Inf)))) + scale_alpha_manual(values=c(0,1),guide="none") + scale_fill_gradient(low="gray99",high="black") + theme_minimal()

noMang <- plotfig(sim); plotParams(noMang)
fish <- plotfig(fishmpa); plotParams(fish)
cons <- plotfig(consmpa); plotParams(cons)
```

### 2014-06-09 Simluations/Figures/compareCatch.Rmd
finished simulations

# for synced online github data
  x = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/noMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL25vTVBBbm90VGhyZXNoX2FkZF8yMDEzLTEyLTA5LmNzdiIsImV4cGlyZXMiOjEzOTEyNjg5OTB9--e041d4ef68764b1fc49140c128bda685c6f740f3")
  sim = read.csv(textConnection(x))

  fish = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/fishMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2Zpc2hNUEFub3RUaHJlc2hfYWRkXzIwMTMtMTItMDkuY3N2IiwiZXhwaXJlcyI6MTM5MTI2OTAzM30%3D--f35f2593a7e901c900188fadca920fdd68a57e35")
  fishmpa = read.csv(textConnection(fish))

  cons = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/consMPAnotThresh_add_2014-01-23.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2NvbnNNUEFub3RUaHJlc2hfYWRkXzIwMTQtMDEtMjMuY3N2IiwiZXhwaXJlcyI6MTM5MTI2OTA3Mn0%3D--ffb8451d33daaeab48f8b3be3357cacbda0aadbb")
  consmpa = read.csv(textConnection(cons))

>>>>

# for synced online github data
   x = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/noMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL25vTVBBbm90VGhyZXNoX2FkZF8yMDEzLTEyLTA5LmNzdiIsImV4cGlyZXMiOjEzOTI2NDYxMDl9--46e45a3eb2faef7fc22b6124253c925bd2290de9")
  sim = read.csv(textConnection(x))

  fish = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/fishMPAnotThresh_add_2013-12-09.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2Zpc2hNUEFub3RUaHJlc2hfYWRkXzIwMTMtMTItMDkuY3N2IiwiZXhwaXJlcyI6MTM5MjY0NjE0NH0%3D--8eff4ee16d08efcf6b266c3e4e42adde7aeff969")
  fishmpa = read.csv(textConnection(fish))

  cons = getURL("https://raw.github.com/emfuller/MovingFish/master/Simluations/Aspatial_fast/Data/nothresh/consMPAnotThresh_add_2014-01-23.csv?token=3235371__eyJzY29wZSI6IlJhd0Jsb2I6ZW1mdWxsZXIvTW92aW5nRmlzaC9tYXN0ZXIvU2ltbHVhdGlvbnMvQXNwYXRpYWxfZmFzdC9EYXRhL25vdGhyZXNoL2NvbnNNUEFub3RUaHJlc2hfYWRkXzIwMTQtMDEtMjMuY3N2IiwiZXhwaXJlcyI6MTM5MjY0NjE2Nn0%3D--586d3cb31ac0f1fe3c49f48886e3796b5132bb77")
  consmpa = read.csv(textConnection(cons))
